Stateless Model Checking with Data-Race Preemption Points

### 2015-10-13 pldi-16/evaluation.tex
nail down contributes and work on eval description a bit

% TODO: Don't forget to add to quicksand a feature to print time-when-job-started (ie, tell total time from test start to bug found in a DR state space == job-start time + job-elapsed time)
% TODO ******BEFORE****** you begin running experimence en masse!

@@

@@

% TODO: List test programs that were run.

@@

{\bf Finding bugs missed by SSS-MC.}
% TODO describe

{\bf Avoiding false positive data-race candidates.}
% TODO describe

@@

>>>>

@@

				% But to be fair, you have to count how many DRs are reported as "couldn't test these, check yourself" at the end.

@@

\newcommand\mxtest{\texttt{mx\_test}}
\newcommand\tej{\texttt{thr\_exit\_join}}
\newcommand\bct{\texttt{broadcast}}
\newcommand\paraguay{\texttt{paraguay}}
\newcommand\paradise{\texttt{paradise\_lost}}
\newcommand\rwl{\texttt{rwl\_test}}
We tested P2s with 6 multithreaded programs:
% from the 410 test suite % XXX: I would like to say this but this is a lie; figure out what else i can say instead
% each tailored to exercise a different part of the P2 project
\mxtest, for locking algorithm correctness, \tej, a test of thread lifecycle, \bct~and \paraguay, for condvars, \paradise~for semaphores, and \rwl~for r/w locks.
For \mxtest~we enabled \landslide's special lock-testing option, which changes the lock-set tracking to consider accesses within {\tt mutex\_lock} and {\tt mutex\_unlock} as data-race candidates.
(Normally, they are considered protected by the very lock they implement: assuming the locks are already correct to enable productive data-race analysis on the rest of the codebase.)
\newcommand\prisema{\texttt{priority\_sema}}
\newcommand\waitsimple{\texttt{wait\_simple}}
% TODO: Add more test cases
We tested the Pintoses with 2 programs from the class test suite: \prisema, a test of the kernel scheduling algorithm, and \waitsimple, a test of process lifecycle. % TODO talk more about these.
In total, this test suite comprises {\large \bf 99999} % TODO
unique state spaces.

All tests were run on 12-core 3.2 GHz Xeon machines with 12GB of RAM.
\quicksand~tests were given 10 CPUs for 1 hour each.
To compare to SSS-MC, we ran a control experiment for each test, running \landslide~on a single state space with all PPs enabled in advance (and no data-race PPs).
% TODO figure out somewhere to mention what landslide's pps are: mx lock/unlock (aka sema up/down)
Though \landslide~does not implement parallel DPOR \cite{parallel-dpor}, we leveled the playing field by giving each control 1 CPU for 10 hours and dividing all associated times by 10 (simulating perfect parallelism).

@@

\begin{table}[t]
	\begin{tabular}{l|l|l}
			& QS bugs & SSS-MC bugs \\
		\hline
		\mxtest & eg 1000 & eg 0 \\
		\bct & & \\
		etc... & & \\
		\hline
		Total & & \\
	\end{tabular}
	\caption{Comparison of all bugs found, broken down by test case, among all P2s (top 6) and Pintoses (bottom {\bf \large 9999999})}
	\label{tab:allbugs}
\end{table}

\begin{table}[t]
	\small
	\begin{tabular}{l|l|l||l|l}
	& QS bug & \begin{tabular}{c} SSS-MC \\ completed\end{tabular}
	& QS bug & \begin{tabular}{c}SSS-MC \\ timeout \end{tabular} \\
		\hline
		\mxtest & e.g. 5 & 10 & 0 & 0 \\
		\bct & & & & \\
		etc... & & & & \\
		\hline
		Total & & & & \\
	\end{tabular}
	\caption{Bugs requiring data-race PPs to expose, found by \quicksand but missed by the single-state-space approach.}
	\label{tab:drbugs}
\end{table}

{\bf Finding bugs missed by SSS-MC.}
Though state-of-the-art MCs preempt only on synchronization events, many serious concurrency bugs are caused by data races leading to corrupted shared state.
In Table~\ref{tab:drbugs} we count ...... % TODO

In Table~\ref{tab:allbugs} .... %TODO

{\bf Avoiding false positive data-race candidates.}
% Though we mechanically verify whether each data race candidate leads to a bug, each new PP can increase combinatorially..... obviously wish to avoid...

@@

\subsection{Discussion} % and future work?

% TODO: Mention that SSSMC control never FAB in mutex_test whatsoever, while DR PPs enabled FABs.

### 2015-10-13 pldi-16/intro.tex
nail down contributes and work on eval description a bit

% TODO fix dis when rest of paper is done
This paper makes {\Large \em ELEVENTYBILLION} contributions:
\begin{enumerate}
	\item Iterative deepening wrapper
	\item Data race tricks, including a false-positive reduction optimization that only works in the context of stateless model checking
	\item Techniques for detecting and flattening cyclic state spaces resulting from ad-hoc while-loop synchronization % TODO: is there actually room for this in the paper?
		% don't forget the maybe_unblock cleverness
	\item Evaluation (elaborate obv)
\end{enumerate}

>>>>

This paper's contributions are as follows:
\begin{enumerate}
	\item Iterative Deepening, a new technique for combining data-race analysis with stateless model checking, and \quicksand, an open source implementation;
	\item A new tactic for eliminating false-positive data race reports, unsound in single-pass analysis but which we prove sound when used with Iterative Deepening;
	%\item Techniques for detecting and flattening cyclic state spaces resulting from ad-hoc while-loop synchronization % TODO: is there actually room for this in the paper?
	\item A large evaluation in which \quicksand~compares favorably to stand-alone data-race detection and stateless model checking approaches.
\end{enumerate}
